ClaTex: LaTeX as a Service on the Cloud

### 2017-05-02 paper.tex
mac update

According to the experiments shown in Wang\cite{Wang2016Dynamic}, Gems, Milc and Mcf in SPEC2006 shows high overhead. We also randomly pick five of SPEC 2006 benchmark, Cactus, Soplex, lbm, sjeng and omnetpp. Besides, we choose our own fake benchmark. We test these benchmark in our environment using 64 hot page set size and sampling rate of $1/128$. As shown in Table \ref{table4}, Gems, Milc, Mcf Omnetpp have high overhead and another five benchmark's performance is good, less than or equal to 3\% overhead. We expect our monitoring system don't impact virtual machine's performance too much. 3\% overhead is still acceptable. But higher overhead is not acceptable. In Table \ref{table4}, we find a phenomenon that the benchmark whose page fault rate is less than $1*10^6$ show better performance. That's a hint to control the overhead of our monitoring system in an acceptable range. A page fault means a context switch from virtual machine to VMM which is a time-consuming work. So we need a mechanism to control the ratio between page fault counts and memory access counts in order to reduce the context switch number significantly.

Page fault's ratio is important factor to contrl our system's overhead. We need a good demarcation point M to judge our system's performance. Experiments\ref{table4} shows $1*10^-6$ is a suitable value. We call this value Sr. If in last period, page fault's ratio is greater than M, we need to decrease tracking rate. If we define $\frac{1}{T}$ as our tracking rate and define r as the ratio between page fault count and memory count, we get the following equation.
\begin{equation}
T = T + 128 \qquad if\;\; r>Sr
\end{equation}

This method works well for large working set benchmark such as Gems. At the first monitoring periods, page fault ratio is larger than $\frac{1}{M}$ and tracking rate decreases from $\frac{1}{128}$ to $\frac{1}{1280}$. Figure \ref{fig8} shows how tracking rate decreases. The overall overhead of Gems is reduced from 7.2\% to 2.3\%. However, it takes 10 periods which means 50 seconds to reduce tracking rate to suitable value. The shortages of the lagging are the slowdown at first part of the benchmark. An intuitive idea is that the greater the distance between the actual page fault ratio and standard scale, the faster the tracking rate drops. We need an exponential drop algorithm\ref{alg2} rather than a linear algorithm. Gems is also tested and it only takes 4 periods reducing tracking rate shown in Figure \ref{fig9}. The overall cost is further reduced to 0.84\%.
\begin{equation}
T = T + 128 * (\log(\frac{r}{Sr}) + 1) \qquad if\;\; r>Sr
\end{equation}
\label{alg2}

@@

In another situation whose memory access pattern is in real workload, we draw the miss curve by AET model and LRU model. Since our monitoring period is 5 seconds, there are too many MRC graph to show in this paper. We pick up some MRC curve randomly when running the benchmark as show in Figure \ref{fig6}. In real workload, page's reuse distance is almost less than reuse time because of the locality. Pages that are current used will be likely reused soon. AET's model obtains approximate result. With MRC curve, we can define working set easily. If we take 5\% miss rate's memory as working set, we can draw a working set changing graph. To evaluate AET model's overall accuracy, we draw working set changing graph using LRU model too. As shown in Figure \ref{fig5}, there are some errors in AET model.

>>>>

According to the experiments shown in Wang\cite{Wang2016Dynamic}, Gems, Milc and Mcf in SPEC2006 shows high overhead. We also randomly pick five of SPEC 2006 benchmark, Cactus, Soplex, lbm, sjeng and omnetpp. Besides, we choose our own fake benchmark. We test these benchmark in our environment using 64 hot page set size and sampling rate of $1/128$. As shown in Table \ref{table4}, Gems, Milc, Mcf， Omnetpp have high overhead and another five benchmark's performance is good, less than or equal to 3\% overhead. We expect our monitoring system don't impact virtual machine's performance too much. 3\% overhead is still acceptable. But higher overhead is not acceptable. In Table \ref{table4}, we find a phenomenon that the benchmark whose page fault rate is less than $1*10^6$ show better performance. That's a hint to control the overhead of our monitoring system in an acceptable range. A page fault means a context switch from virtual machine to VMM which is a time-consuming work. So we need a mechanism to control the ratio between page fault counts and memory access counts in order to reduce the context switch number significantly.

Page fault's ratio is important factor to contrl our system's overhead. We need a good demarcation point to judge our system's performance. Experiments\ref{table4} shows $1*10^-6$ is a suitable value. We call this value Sr. If in last period, page fault's ratio is greater than Sr, we need to decrease tracking rate. If we define $\frac{1}{T}$ as our tracking rate and define r as the ratio between page fault count and memory count, we get the following equation.
\begin{equation}
T = T + 128 \qquad if\;\; r>Sr
\end{equation}

This method works well for large working set benchmark such as Gems. At the first monitoring periods, page fault ratio is larger than $Sr$ and tracking rate decreases from $\frac{1}{128}$ to $\frac{1}{1280}$. Figure \ref{fig8} shows how tracking rate decreases. The overall overhead of Gems is reduced from 7.2\% to 2.3\%. However, it takes 10 periods which means 50 seconds to reduce tracking rate to suitable value. The shortages of the lagging are the slowdown at first part of the benchmark. An intuitive idea is that the greater the distance between the actual page fault ratio and standard scale, the faster the tracking rate drops. We need an exponential drop algorithm\ref{alg2} rather than a linear algorithm. Gems is also tested and it only takes 4 periods reducing tracking rate shown in Figure \ref{fig9}. The overall cost is further reduced to 0.84\%.
\begin{equation}
T = T + 128 * (\log(\frac{r}{Sr}) + 1) \qquad if\;\; r>Sr
\end{equation}
\label{alg2}

@@

In another situation whose memory access pattern is in real workload, we draw the miss curve by AET model and LRU model. Since our monitoring period is 5 seconds, there are too many MRC graph to show in this paper. We pick up some MRC curve randomly when running the benchmark as show in Figure \ref{fig6}. In real workload, page's reuse distance is almost less than reuse time because of the locality. Pages that are current used will be likely reused soon. AET's model obtains approximate result. With MRC curve, we can define working set easily. If we take 5\% miss rate's memory as working set, we can draw a working set changing graph. To evaluate AET model's overall accuracy, we draw working set changing graph using LRU model too. As shown in Figure \ref{fig5}, there are some errors in AET model.%%这一段要大改！！！
